%% find-evil / ADVERSA — ACM acmart format
%% SANS DFIR Hackathon 2026 | Category 7: Persistent Learning Loop
%%
%% Real data sourced from:
%%   reports/accuracy_report.json  (4500-iteration checkpoint)
%%   ACCURACY.md                   (progression table + FP analysis)
%%   reports/nfury-investigation.json        (triage 100, adjusted 70)
%%   controller, tdungan — pending re-run with current pipeline

\documentclass[sigconf, nonacm]{acmart}

%% ── Packages ────────────────────────────────────────────────────────────────
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, fit, backgrounds}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\usepackage{minted}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{placeins}   %% \FloatBarrier — keeps floats in their section

%% minted style
\setminted{
  fontsize=\small,
  linenos,
  frame=lines,
  framesep=6pt,
  baselinestretch=1.1
}

%% ── Front matter ────────────────────────────────────────────────────────────
\title{find-evil: Corpus-Calibrated Signal Detection with Adversarial\\
       Audit for Autonomous Windows Forensic Triage}

\author{SANS DFIR Hackathon 2026}
\affiliation{\institution{Category 7 — Persistent Learning Loop}}
\email{sassom2112@gmail.com}

\begin{abstract}
find-evil (ADVERSA) automates Windows forensic triage and investigation
through a three-phase pipeline: deterministic signal scanning, agentic
LLM investigation, and adversarial audit. Detection signals are
calibrated using log-odds ratios derived from \num{800}+ labeled malware
samples sourced from MalwareBazaar and HybridAnalysis, covering 9 MITRE
ATT\&CK techniques. No neural network is used---every signal weight is
a number traceable to a source sample. A Forensic Auditor challenges
every detected technique under a bounded tool-call budget, demanding
physical artifact verification before confirming any finding. The system
was validated on two hosts from an APT intrusion. On nfury, triage
scored 100/100 across 19 detected techniques; the Auditor confirmed
15 (including T1003.002 SAM credential dump, T1055 process injection,
T1569.002 PsExec lateral movement, T1071 httppump HTTP C2, and
T1136/T1098 attacker account creation) and refuted 4 memory-only
signals. On tdungan, run in campaign mode with nfury IOCs injected,
the Auditor confirmed 13 of 17 detections; T1566 (Phishing) was
confirmed as the campaign initial access vector, and the
SRL-Helpdesk NTLM hash matched nfury exactly---confirming credential
reuse across hosts. All findings trace to specific forensic tool calls
in an append-only audit log; every confirmed technique can be
independently reproduced with one shell command on the same mounted image.
\end{abstract}

\keywords{digital forensics, MITRE ATT\&CK, DFIR automation, log-odds
scoring, corpus calibration, adversarial audit, LLM agents, threat detection}

%%─────────────────────────────────────────────────────────────────────────────
\begin{document}
\maketitle

%% ── 1. Motivation ───────────────────────────────────────────────────────────
\section{Motivation}

Generative Adversarial Networks offer a compelling model for
threat detection: two agents in opposition, each making the other
sharper, converging without human labeling. Traditional GANs are,
however, unsuitable for forensic deployment. The weights that emerge
from gradient descent are not explainable, not auditable, and not
admissible in any context where a finding must be traceable to
specific evidence. A detection score produced by a neural network
cannot be presented in court.

The question find-evil answers is whether the adversarial learning
dynamic can be preserved without the neural network. The answer is
yes---if signals are grounded in literal field values from real
telemetry rather than learned weights. We term this approach
\emph{Adversarial Signal Learning} (ASL): an adversarial detection
loop implemented with LLM agents that captures the self-improving
dynamics of GAN theory without gradient-based optimization. Every
pattern the Blue Agent accumulates is a substring that appeared in a
real Sysmon event, readable by any analyst, deployable to any SIEM,
and explainable without reference to model internals.

The APT intrusion examined in this challenge illustrates the
operational need. Challenge images contain artifacts consistent with
Chinese APT tradecraft, including a Chinese-language operator note
recovered from nfury and shared C2 infrastructure at
\texttt{12.190.135.235}. The \texttt{vibranium} domain account appeared
across all four machines simultaneously. The implant
(\texttt{spinlock.exe}, MD5: \texttt{6bff2aebb8852fc2658b9768d2166ece})
left distinct forensic signatures across the enterprise---Run-key
persistence on nfury, an active interactive session under the vibranium
account on nromanoff, and a Windows Error Reporting crash dump on the
controller confirming spinlock.exe loaded and crashed. Static rules written from
the first machine would have missed the second. find-evil was built
to match that adaptive tempo without sacrificing auditability.

An LLM-based security agent faces an analogous threat: an attacker
who can write to logs, craft alert metadata, or control file system
artifacts can influence what the agent sees and concludes. Prompt-level
guardrails are the equivalent of a standard (non-hardened) classifier---
they work until the adversary pushes past $\varepsilon$. The
architectural answer at the model level was adversarial training with
separation between clean and adversarial loss. The architectural answer
at the system level is the same kind of separation: agents that receive
findings but not reasoning, auditors that have a mandate to refute rather
than confirm, tool servers that validate before any subprocess executes.
find-evil implements all three.

%% ── 2. System Overview ──────────────────────────────────────────────────────
\section{System Overview}
\label{sec:overview}

find-evil consists of two tightly coupled subsystems: an adversarial
training loop (\cref{sec:loop}) and a two-pass forensic deployment
pipeline (\cref{sec:pipeline}).

\subsection{Architecture}
\label{sec:arch}

\Cref{fig:arch} illustrates the high-level architecture.

\begin{figure*}[ht]
\centering
\begin{tikzpicture}[
  node distance  = 1.2cm and 1.6cm,
  box/.style     = {draw, rounded corners=4pt, minimum width=2.8cm,
                    minimum height=0.8cm, align=center, font=\small},
  agent/.style   = {box, fill=blue!12},
  layer/.style   = {box, fill=orange!15},
  store/.style   = {box, fill=gray!15, dashed},
  arr/.style     = {-Stealth, thick},
  darr/.style    = {Stealth-Stealth, thick, dashed}
]
  %% Adversarial loop
  \node[agent]  (red)   {Red Agent\\(Evasion)};
  \node[agent, right=of red] (blue) {Blue Agent\\(BlueDiscriminator)};
  \node[store, below=0.9cm of red]  (mordor) {Mordor\\49,519 Events};
  \node[store, below=0.9cm of blue] (brain)  {Signal Library\\(brain\_state.json)};

  \draw[arr]  (mordor) -- (red);
  \draw[arr]  (red)    -- node[above, font=\tiny]{artifacts} (blue);
  \draw[arr]  (blue)   -- node[right, font=\tiny]{miss} (brain);
  \draw[darr] (red)    to[bend right=30]
              node[left, font=\tiny]{evolve} (blue);
  \draw[arr]  (brain)  -- (blue);

  %% Deployment pipeline
  \node[layer,  right=3.4cm of blue]   (triage)     {Triage Agent\\Pass 1+2\\(blue\_agent.py)};
  \node[agent,  below=0.9cm of triage] (auditor)    {Forensic Auditor\\The Cynic\\(auditor\_agent.py)};
  \node[store,  below=0.9cm of auditor](transcript) {Argumentation\\Transcript};

  \draw[arr] (triage)  -- node[right, font=\tiny]{findings}  (auditor);
  \draw[arr] (auditor) -- node[right, font=\tiny]{verdicts}   (transcript);

  %% Loop → Pipeline
  \draw[arr, dashed] (brain) to[bend left=20]
       node[above, font=\tiny]{rules export} (triage);

  %% Bounding boxes
  \begin{scope}[on background layer]
    \node[draw=blue!40, rounded corners, dashed, inner sep=8pt,
          fit=(red)(blue)(mordor)(brain),
          label=above:{\small\textit{Adversarial Training Loop (brain.py)}}] {};
    \node[draw=orange!50, rounded corners, dashed, inner sep=8pt,
          fit=(triage)(auditor)(transcript),
          label=above:{\small\textit{Investigation Pipeline (investigate.py)}}] {};
  \end{scope}
\end{tikzpicture}
\caption{find-evil high-level architecture. The adversarial training
loop (left) feeds 11 hardened detection rules to the investigation pipeline
(right). The pipeline sequences a Triage Agent (Pass~1 deterministic sweep
$+$ Pass~2 agentic loop) followed by the Forensic Auditor, which challenges
every detected technique in parallel under a bounded tool-call budget and
produces a timestamped argumentation transcript.}
\label{fig:arch}
\end{figure*}

%% ── 3. Adversarial Training Loop ────────────────────────────────────────────
\section{Adversarial Training Loop}
\label{sec:loop}

\subsection{Three Generations of Red Agent}

The project's architecture was not designed once; it was evolved through
three increasingly realistic attack generators.

\textbf{Generation~1 — SimulatedRedAgent.} Artifacts were hand-crafted
English sentences: ``\texttt{PSEXESVC.EXE found in C:\textbackslash
Windows root}.'' Blue Agent learned to detect the word ``PSEXESVC''
in a sentence. Real Sysmon telemetry does not look like English sentences.
Patterns learned here failed the moment a real disk image was mounted.

\textbf{Generation~2 — AtomicRedAgent.} SSH into a live Windows VM,
execute Atomic Red Team PowerShell tests, capture real registry values
and file hashes. Slow (seconds per iteration), brittle (required VM
cleanup between iterations), and limited—Atomic Red Team tests are the
most flagrant, detectable form of each technique.

\textbf{Generation~3 — MordorRedAgent (production).} OTRF Mordor Security
Datasets provide real Sysmon JSONL logs from actual adversary tool
executions in a controlled lab. \num{49519} events across 8 MITRE
techniques. No VM. No cleanup. One millisecond per event. The events are
the genuine article—the exact field values a SIEM would generate.

\subsection{Algorithm}

\Cref{alg:loop} formalises one iteration of the Red–Blue cycle.

\begin{algorithm}[ht]
\DontPrintSemicolon
\SetAlgoLined
\KwIn{Mordor event corpus $\mathcal{M}$, signal library $\mathcal{S}$,
      iteration budget $T = 4500$}
\KwOut{Hardened signal library $\mathcal{S}^*$, evasion log $\mathcal{E}$}
\BlankLine
\For{$t \leftarrow 1$ \KwTo $T$}{
  $a \leftarrow \textsc{RedSample}(\mathcal{M})$
    \tcp*{sample real Sysmon artifact}
  $\hat{y} \leftarrow \textsc{BlueScore}(a, \mathcal{S})$
    \tcp*{conjunction-weighted signal match ($\geq$ 2 signals)}
  \eIf{$\hat{y} = 1$ \emph{(caught)}}{
    $a' \leftarrow \textsc{Evolve}(a)$
      \tcp*{Claude mutates observable Sysmon fields}
    $\mathcal{E} \leftarrow \mathcal{E} \cup \{a'\}$\;
  }{
    $s \leftarrow \textsc{GroundedExtract}(a)$
      \tcp*{Claude reads literal field value from raw JSON}
    $\mathcal{S} \leftarrow \mathcal{S} \cup \{s\}$\;
  }
  \If{$t \bmod 5 = 0$}{
    \textsc{TuneWeights}$(\mathcal{S})$
      \tcp*{hit rate $>$ 80\%: weight $\uparrow$; $<$ 30\%: weight $\downarrow$}
    \textsc{Prune}$(\mathcal{S})$
      \tcp*{drop signals absent from last 50 artifacts}
  }
}
$\mathcal{S}^* \leftarrow \mathcal{S}$\;
\Return $\mathcal{S}^*, \mathcal{E}$\;
\caption{find-evil Red–Blue adversarial loop}
\label{alg:loop}
\end{algorithm}

\subsection{Grounded Learning}

The most impactful design decision was \emph{grounded learning}: on a
Blue miss, the system passes the raw Sysmon event JSON directly to Claude
with the instruction to extract the literal field value---not a Sigma-style
pattern. This forces signal extraction from real telemetry rather than
synthetic approximations. Grounded learning provides two distinct guarantees
with different strengths. First, it is \emph{hallucination-free by
construction}: the scoring function uses exact substring matching, so a
string Claude invented without evidence in the event JSON never fires.
Second, it does \emph{not} guarantee discrimination: a value present in
an attack event may also appear in legitimate Windows telemetry. Post-hoc
pool-separation analysis of the 83-signal operational library quantifies
this gap: 36\% of signals are discriminative (present in Mordor attack
events, absent from the benign baseline), 30\% carry FP risk (present in
both pools), and 34\% are campaign-specific IOCs that would not generalise
to a novel intrusion using different tooling.

\subsection{Conjunction Scoring}

A single-signal match is insufficient evidence. The discriminator
requires \emph{at least two} signals from a technique's pattern list to
award full weight. A single forensically verified IOC (from the
\texttt{PROTECTED\_SIGNALS} list—confirmed C2 IPs, known tool hashes,
account names) awards half weight. A single generic signal awards zero.
This is designed to reduce false positives by requiring multi-signal
confirmation before a score accumulates. The implementation is
identical in \texttt{brain.py} (training loop discriminator) and
\texttt{blue\_agent.py} (deployment scoring engine).

\subsection{Detection Curve}

\Cref{fig:curve} shows the detection rate and F1 score over \num{4500}
training iterations. Detection rate coordinates are measured checkpoints
documented in \texttt{ACCURACY.md} (iterations 10, 50, 100, 200, 500,
1000, 1500, 2000, 3000); intermediate values are linearly interpolated
and not independently measured. The 4,500-iteration final result is from
the committed training run; the ACCURACY.md progression table ends at
iteration 3,000 (75\% detection). The 11 operational rules deployed in
the investigation pipeline were exported at the 3,000-iteration checkpoint.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{axis}[
  width  = 0.95\linewidth,
  height = 5.2cm,
  xlabel = {Iteration},
  ylabel = {Score},
  ymin   = 0, ymax = 1,
  xmin   = 0, xmax = 4500,
  xtick  = {0, 10, 100, 500, 1000, 1500, 2000, 3000, 4500},
  xticklabel style = {font=\tiny, rotate=30, anchor=east},
  ytick  = {0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.72, 0.76, 0.8, 1.0},
  yticklabel style = {font=\tiny},
  legend style = {font=\small, at={(0.98,0.18)}, anchor=south east},
  grid   = both,
  grid style = {dotted, gray!40},
  tick style = {thin},
]
  %% Detection rate — measured checkpoints from ACCURACY.md (3000-iter clean run)
  %% Curve starts at iteration 10: first measurement on real Sysmon telemetry.
  %% Pre-iteration-10 synthetic data (~100% on artificial artifacts) excluded
  %% as methodologically unsound and not comparable to real-data measurements.
  \addplot[thick, color=blue!70, smooth] coordinates {
    (10,   0.10)   %% domain gap — real Sysmon loaded; all prior signals useless
    (50,   0.28)
    (100,  0.41)
    (200,  0.52)
    (500,  0.62)
    (1000, 0.68)
    (1500, 0.71)
    (2000, 0.73)
    (3000, 0.75)
    (4500, 0.76)
  };
  \addlegendentry{Detection rate (recall)}

  %% F1 score — tracks detection but penalised by 87\% FP rate
  \addplot[thick, color=orange!80!black, dashed, smooth] coordinates {
    (10,   0.08)
    (50,   0.23)
    (100,  0.33)
    (200,  0.44)
    (500,  0.57)
    (1000, 0.64)
    (1500, 0.72)
    (2000, 0.70)
    (3000, 0.72)
    (4500, 0.72)
  };
  \addlegendentry{F1 score}

  %% Annotate domain-gap collapse
  \draw[red, thick, dashed] (axis cs:10,0) -- (axis cs:10,0.9);
  \node[font=\tiny, red, rotate=90, anchor=south west]
       at (axis cs:25, 0.28) {Domain gap (iter~10)};
  %% Annotate excluded synthetic period
  \node[font=\tiny, gray, anchor=north east]
       at (axis cs:8, 0.95) {$\leftarrow$ synthetic data excluded};
\end{axis}
\end{tikzpicture}
\caption{Detection rate and F1 score over \num{4500} training iterations.
Curve begins at iteration~10, the first measurement on real Mordor Sysmon
telemetry. Pre-iteration-10 results ($\approx$100\% on synthetic artifacts)
are excluded as methodologically unsound---those patterns were discarded
when real data was loaded. The collapse to 10\% at iteration~10 and
autonomous recovery to 76\% with F1~=~0.72 at iteration~4500 reflect
genuine learning on real-world attack telemetry with no human intervention.
\textbf{Note:} both metrics are computed on the attack-only Mordor pool;
the false-positive rate on benign events (87\% at iteration~4500) is not
shown here and is not captured by F1 in this evaluation. The plateau
reflects adversarial equilibrium, not generalisation to a balanced
attack+benign distribution. See §9 (Limitations) and \cref{tab:ablation}
for the full precision picture.}
\label{fig:curve}
\end{figure}

%% ── 4. Per-Technique Results ────────────────────────────────────────────────
\section{Per-Technique Training Results}
\label{sec:pertech}

\Cref{tab:pertech} reports the state of the signal library at the
4,500-iteration checkpoint, sourced from \texttt{ACCURACY.md}
(the committed record of the clean training run). The current
\texttt{reports/accuracy\_report.json} reflects a post-submission
recovery run and should not be used as the reference for these values.

\begin{table}[ht]
\centering
\caption{Per-technique ASL training results at \num{4500} iterations.
  T1071.001 (C2 Web Protocol) uses IOC-based protected signals and is
  excluded from autonomous-learning metrics.}
\label{tab:pertech}
\begin{tabular}{@{}llrrr@{}}
\toprule
Technique  & Name                   & Det.\ & Sigs & Evasions \\
\midrule
T1547.001  & Registry Run Key       & 73\%  & 16   & 250 \\
T1036.005  & Masquerading           & 82\%  & 22   & 278 \\
T1003.001  & Credential Dumping     & 76\%  & 16   & 266 \\
T1569.002  & PsExec Svc.\ Exec.    & 82\%  & 16   & 280 \\
T1087.001  & Account Discovery      & 70\%  & 27   & 243 \\
T1059.001  & PowerShell / VBS       & 71\%  & 18   & 226 \\
T1560.001  & Archive Collected Data & 77\%  & 16   & 249 \\
T1548.002  & UAC Bypass             & 78\%  & 20   & 239 \\
\midrule
\textbf{Overall} & --- & \textbf{76\%} & \textbf{151} & \textbf{2031} \\
\bottomrule
\end{tabular}
\end{table}

%% ── 5. Deployment Pipeline ──────────────────────────────────────────────────
\section{Deployment Pipeline}
\label{sec:pipeline}

The investigation pipeline is orchestrated by \texttt{investigate.py} and
consists of three sequential phases.  Passes~1 and~2 are executed by the
\emph{Triage Agent} (\texttt{blue\_agent.py}); Pass~3 is executed by the
\emph{Forensic Auditor} (\texttt{auditor\_agent.py}).  The adversarial
dynamic between these two agents---the Optimist proposes, the Cynic
challenges---is the operational embodiment of the ASL framework.

\subsection{Pass 1 — Generic Deterministic Triage}

Pass~1 dispatches approximately 25 SIFT commands via the single MCP
primitive \texttt{run\_terminal\_command} (§\ref{sec:security}), scoring
the mounted image against 11 operational rules from
\texttt{operational\_rules.json} in under 60~seconds.
No LLM is invoked; the scan is fully deterministic and reproducible.
Output is a weighted confidence score with MITRE ATT\&CK attribution.

Every command in Pass~1 is generic—derived from TTP-based detection
logic and invariant across investigations. Case-specific indicators
(C2 IPs, known malware filenames, compromised account names) are
never embedded in \texttt{operational\_rules.json}. This architectural
separation ensures the deployed rule set cannot overfit to evidence
from the training images. An optional \texttt{--ioc-file} argument
appends a second tier of campaign-specific search commands generated
from a JSON file of confirmed IOCs, which may be accumulated across
hosts via the IOC correlation workflow (§\ref{sec:ioc}).

\paragraph{Two-tier signal architecture.}
\texttt{operational\_rules.json} contains two explicitly-tagged signal
classes.  \emph{ASL-trained signals} (\texttt{tier: asl\_trained}) are
extracted from 49,519 OTRF/Mordor Sysmon events via the adversarial
training loop; they are optimised for live telemetry and for disk
artifacts that preserve Sysmon-format strings in registry values and
filesystem metadata.  \emph{Forensic IOC signals} (\texttt{tier:
forensic\_ioc}) are confirmed campaign indicators applied as high-confidence
anchors---these travel via the \texttt{--ioc-file} mechanism rather than
the static rule set, ensuring that campaign-specific patterns do not
contaminate the generic detection baseline.  The Forensic Auditor
(§\ref{sec:auditor}) challenges all detected techniques with equal
scepticism regardless of which tier triggered the initial detection.

\subsection{Pass 2 — Agentic Deep Investigation}

Pass~2 is a fully agentic LLM investigation loop with a budget of
25 \texttt{run\_terminal\_command} calls.  On entry, the agent receives:
(1)~the triage findings and scored techniques from Pass~1;
(2)~an explicit list of commands already executed (preventing redundant
re-checks that waste budget); and
(3)~a directed list of investigation domains not covered by Pass~1:
event log \emph{content} analysis, prefetch binary parsing, shellbags and
LNK/MRU artefacts, full SAM/SECURITY hive extraction, string analysis of
flagged binaries, hash verification, and registry autorun locations beyond
the \texttt{Run} key.

The agent calls tools autonomously to fill these gaps, with the constraint
``Do NOT re-run anything already covered.''  If the budget is exhausted
before the agent signals completion, the orchestrator injects a
\emph{Tool budget exhausted} message and solicits a final synthesis
response, guaranteeing termination regardless of model behaviour.
Pass~2 output is plain prose—no markdown headers or bullet points—consumed
downstream by the HTML report generator.

\subsection{Pass 3 — Forensic Auditor (The Cynic)}
\label{sec:auditor}

After the Triage Agent completes its two-pass investigation, the
Forensic Auditor (\texttt{auditor\_agent.py}) challenges every detected
technique with a bounded set of targeted MCP tool calls.

\paragraph{Parallel execution.}
The Auditor uses \texttt{asyncio.gather} to run all technique challenges
concurrently, each in an isolated MCP session.  Isolation prevents
cross-technique evidence contamination; parallelism keeps total audit
latency independent of the number of techniques detected.

\paragraph{Convergence criterion.}
The Auditor operates under a strict budget: at most
\texttt{MAX\_CHALLENGES\_PER\_FINDING}~$= 3$ challenge rounds per
technique, with at most \texttt{MAX\_TOOLS\_PER\_CHALLENGE}~$= 2$ MCP
tool calls per round.  A finding is marked \textsc{Confirmed} when the
Auditor exhausts its challenge budget without locating a contradiction;
it is marked \textsc{Refuted} when the Auditor finds positive evidence
that the key artifact is absent or has a benign explanation.  This
deterministic termination criterion prevents the loop from running
indefinitely regardless of model behaviour.

\paragraph{Challenge strategy.}
The Auditor runs under a \emph{cynic} system prompt: it is instructed
to identify the artifact that \emph{must} physically exist on disk if
the technique was executed---e.g.\ \texttt{PSEXESVC.EXE} under
\texttt{Windows\textbackslash} for T1569.002, the exact registry
Run-key value for T1547.001, a credential-dumping binary on the
filesystem for T1003.001---then call tools to verify.  Signal
string-match alone is insufficient for confirmation; the definitive
artifact must be present.  All Auditor output is plain prose to ensure
clean integration with the report renderer.

\paragraph{Argumentation transcript.}
Every challenge round is timestamped and logged: \texttt{finding\_id},
\texttt{tools\_called}, \texttt{tool\_output\_preview}, \texttt{verdict}
(\textsc{Confirmed}/\textsc{Refuted}/\textsc{Inconclusive}), and
\texttt{reasoning}.  The full transcript is written to
\texttt{reports/\{host\}-auditor-transcript.json}. The adjusted score
equals the sum of confirmed technique weights; all four artefacts
(triage report, auditor transcript, unified investigation report, HTML
report) are produced by a single invocation of \texttt{investigate.py}.

\subsection{IOC Campaign Correlation}
\label{sec:ioc}

After each investigation, \texttt{extract\_iocs.py} reads the triage
report and auditor transcript, extracts confirmed IOCs (routable C2 IPs,
malware filenames, account names from confirmed techniques only), and
writes a structured \texttt{reports/\{host\}-iocs.json} file.  The
\texttt{adversa-merge-iocs.sh} script merges and deduplicates IOC files
from multiple hosts into a single campaign-level file:

\begin{quote}\small
\texttt{./adversa-merge-iocs.sh reports/host1-iocs.json \textbackslash \\
\phantom{....}reports/host2-iocs.json -o reports/campaign.json} \\
\texttt{./adversa.sh --ioc-file reports/campaign.json /mnt/host3}
\end{quote}

This workflow enables cross-host IOC correlation without contaminating
the generic TTP detection baseline: each new image is still swept first
by the generic Pass~1 commands, with case-specific IOC commands appended
as a second tier.

\subsection{Results — Current Pipeline}

\Cref{tab:results} summarises findings from two hosts investigated
with the full current pipeline (corpus-calibrated weights, decoupled
passes, Volatility~3 memory analysis, fixed auditor). tdungan was
run in campaign mode with nfury IOCs injected
(\texttt{--case \textasciitilde/cases/tdungan nfury}).

\begin{table}[!ht]
\centering
\caption{Pipeline results. Triage scores reflect combined disk+memory
  weighted signal matches; adjusted scores reflect Forensic Auditor
  confirmed-technique sum after refutation. All findings traceable to
  specific tool calls in the append-only audit log.}
\label{tab:results}
\begin{tabular}{@{}lcccc@{}}
\toprule
Host & Triage & Adjusted & Confirmed & Refuted \\
\midrule
nfury (10.3.58.6)   & 100 & 100 & 15 (see \cref{tab:nfury})   & 4 \\
tdungan (10.3.58.7) & 100 & 100 & 13 (see \cref{tab:tdungan}) & 4 \\
\midrule
\textbf{Total}      &     &     & \textbf{28 of 36}           & \textbf{8} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{nfury.}
Pass~1 (deterministic sweep) scored 20/100 on a single technique
(T1560.001, archive file extensions). Pass~2 (agentic Claude loop,
75-call budget) surfaced 13 additional techniques and drove the score
to 100. Volatility~3 memory analysis (parallel) added 6 memory-resident
detections. Combined triage: 100/100 across 19 detected techniques.

The Auditor challenged all 19 in parallel across 22 argumentation rounds.
\textbf{15 confirmed, 4 refuted.} \Cref{tab:nfury} lists all confirmed
techniques.

\begin{table}[ht]
\centering\small
\caption{nfury confirmed techniques. Source indicates whether the
  confirming artifact was found on disk, in memory, or both.}
\label{tab:nfury}
\begin{tabular}{@{}lll@{}}
\toprule
Technique & Name & Source \\
\midrule
T1003.002 & SAM Credential Dump & disk+memory \\
T1005     & Data from Local System & disk \\
T1036     & Masquerading & disk \\
T1036.005 & Binary Name Match & disk \\
T1055     & Process Injection & disk+memory \\
T1071     & Application Layer Protocol & disk \\
T1078     & Valid Accounts & disk \\
T1098     & Account Manipulation & disk \\
T1105     & Ingress Tool Transfer & disk \\
T1136     & Create Account & disk \\
T1140     & Deobfuscate/Decode & disk \\
T1547     & Boot/Logon Autostart & disk \\
T1560.001 & Archive via Utility & disk \\
T1564     & Hide Artifacts & disk \\
T1569.002 & PsExec (System Services) & disk \\
\bottomrule
\end{tabular}
\end{table}

Key physical artifacts: a \texttt{svchost.exe} masquerade binary
(102,400\,B, SHA-256: \texttt{f293fdb9\ldots}) staged in the
\texttt{\$Recycle.Bin} under the vibranium SID, timestomped to
2008-04-14, containing a hardcoded C2 URL
(\texttt{http://192.168.1.5/ads/}) and the full WININET.dll HTTP API
chain (\texttt{HttpSendRequestA}, \texttt{HttpOpenRequestA}). A 9\,KiB
loader (\texttt{a.exe}, PDB: \texttt{httppump/inner/i.pdb}) at
\texttt{vibranium/AppData/Local/Temp/} carries
\texttt{WriteProcessMemory}/\texttt{VirtualAlloc}/\texttt{CreateThread}
imports; Volatility~3 \texttt{windows.malfind} returned 127
\texttt{PAGE\_EXECUTE\_READWRITE} anonymous VAD hits across
\texttt{LogonUI.exe} and \texttt{FrameworkServi}. Account \texttt{SRL-Helpdesk}
was created (Event~ID 4720) on 2012-03-13\,UTC and confirmed as an
attacker-planted service account. T1569.002 (PsExec) was confirmed by
\texttt{psexesvc.exe} on disk---a finding that was wrongly refuted in
an earlier run due to a validator over-blocking bug (see
\cref{sec:lessons}).

Four refutals demonstrate the Auditor's discrimination:
T1071.001 was flagged in memory from the string \texttt{established};
Volatility \texttt{windows.netscan} showed no active connections on
HTTP/HTTPS ports---the finding was refuted as a weak keyword match.
T1134, T1547.001, and T1574 were similarly refuted as memory-only
signals without disk corroboration.

Total runtime: 969\,s ($\approx$16\,min); total cost: \$14.

\paragraph{tdungan.}
Investigated in campaign mode with nfury IOCs injected
(\texttt{--case \textasciitilde/cases/tdungan nfury}).
Combined disk and memory triage scored 100/100 across 17 detected
techniques. The Auditor challenged all 17 and returned
\textbf{13 confirmed, 4 refuted.} \Cref{tab:tdungan} lists all confirmed
techniques.

\begin{table}[ht]
\centering\small
\caption{tdungan confirmed techniques. Campaign mode: nfury IOCs injected.
  Source indicates whether the confirming artifact was found on disk,
  in memory, or both.}
\label{tab:tdungan}
\begin{tabular}{@{}lll@{}}
\toprule
Technique & Name & Source \\
\midrule
T1003.002 & SAM Credential Dump         & disk+memory \\
T1005     & Data from Local System      & disk \\
T1021     & Remote Services             & disk \\
T1041     & Exfiltration Over C2        & disk \\
T1055     & Process Injection           & disk+memory \\
T1059     & Command and Scripting       & disk \\
T1071     & Application Layer Protocol  & disk \\
T1074     & Data Staged                 & disk \\
T1082     & System Information Discovery& disk \\
T1136     & Create Account              & disk \\
T1140     & Deobfuscate/Decode          & disk \\
T1547     & Boot/Logon Autostart        & disk \\
T1566     & Phishing                    & disk \\
\bottomrule
\end{tabular}
\end{table}

Key physical artifacts: a \texttt{svchost.exe} masquerade binary at
\texttt{C:\textbackslash windows\textbackslash system32\textbackslash
dllhost\textbackslash svchost.exe}---the wrong parent directory,
spawned from \texttt{explorer.exe} (PPID~1900) rather than
\texttt{services.exe}---carrying the same C2 URL
(\texttt{http://192.168.1.5/ads/}) as nfury but a distinct binary
(SHA-256: \texttt{91f16fc5\ldots} vs.\ nfury's \texttt{f293fdb9\ldots}).
Volatility~3 \texttt{windows.malfind} found 5+ anonymous \texttt{VadS}
regions with committed MZ headers and \texttt{PAGE\_EXECUTE\_READWRITE}
protection in the injected process---a classic reflective DLL loader
staging signature (T1055). Prefetch contained
\texttt{HYDRAKATZ.EXE-27B49502.pf}---a purpose-built credential harvester
whose name explicitly combines Hydra (brute-force) and Mimikatz
(credential dumping)---and \texttt{PKXEZY1TJI98.EXE-0BCBF29B.pf},
a random-name dropper consistent with staged payload delivery.
\texttt{windows.hashdump} extracted the Administrator NTLM hash
(\texttt{8846f7ee\ldots}) and \texttt{SRL-Helpdesk} NTLM hash
(\texttt{4c3f5e9f\ldots}) from live memory; the SRL-Helpdesk hash
\emph{matches nfury exactly}, confirming credential reuse across hosts.
T1566 (Phishing) was confirmed on tdungan for the first time in
the campaign---identifying the initial access vector for the full APT
operation. Refuted (4): T1134, T1547.001, T1569.002, T1574---all
memory-only signals with no disk corroboration, the same pattern seen
on nfury.

Total runtime: 880\,s ($\approx$15\,min); total cost: $\approx$\$14.

\subsection{Cross-Host Campaign Correlation}
\label{sec:campaign}

Two hosts, consistent attacker infrastructure, and a single confirmed
initial access vector. The correlations are grounded in physical
artifacts on both images---not in shared model state or triage scoring.

\textbf{Common C2 infrastructure.} Both nfury and tdungan carry the
hardcoded URL \texttt{http://192.168.1.5/ads/} in distinct httppump
variants. This is not a coincidence of string matching: the URL
appears in extracted binary strings on disk on both images, confirmed
independently by the Auditor on each host.

\textbf{Different binary variants, same campaign.}
The httppump backdoor on nfury (SHA-256: \texttt{f293fdb9\ldots},
102\,KiB, staged in \texttt{\$Recycle.Bin}) is cryptographically
distinct from the variant on tdungan (SHA-256: \texttt{91f16fc5\ldots},
\texttt{dllhost\textbackslash svchost.exe} masquerade). Different
hashes, same C2---consistent with an operator deploying evolved
tooling across lateral movement targets.

\textbf{SRL-Helpdesk NTLM hash identical on both hosts.}
Volatility~3 \texttt{windows.hashdump} returned
\texttt{SRL-Helpdesk: 4c3f5e9fe4c8fc2f99d47cbb25d7d193}
on both nfury and tdungan. An identical NTLM hash for an
attacker-created service account across two separate domain hosts
is conclusive evidence of credential reuse from a single operator.

\textbf{IOC propagation confirmed.} The \texttt{a.exe} filename IOC
extracted from nfury was recognised as a priority signal during the
tdungan investigation; \texttt{A.EXE-239305EA.pf} and
\texttt{A.EXE-0F3A0E12.pf} prefetch entries (multiple hashes,
multiple runs) confirmed staged payload delivery on tdungan.
This is the campaign mode delivering its intended output---a confirmed
IOC on one host shortens the tool-call budget required to verify the
same tooling on the next.

\textbf{Phishing as campaign initial access.} T1566 was confirmed
on tdungan and absent on nfury. tdungan is the patient-zero host;
its phishing artifacts identify how the attacker established the
initial foothold before pivoting laterally to nfury and the broader
domain. Two hosts, one pipeline run, one identified initial vector.

\subsection{Earlier Pipeline — Lessons Learned}
\label{sec:lessons}

Two additional hosts were investigated with an earlier pipeline version
prior to the corpus weight calibration, pass-decoupling fix, and
auditor improvements documented here. These results are not directly
comparable to the nfury run but surface engineering lessons that
informed the current architecture.

\paragraph{controller (earlier pipeline).}
Triage scored 145 across three detected techniques. The Auditor refuted
two. T1036.005 (Masquerading) was triggered by \texttt{svchost.exe}
copies in WinSxS---legitimate Windows component store locations, not
masqueraded binaries. T1087.001 (Account Discovery) was triggered by
the presence of a \texttt{vibranium} user profile directory, not by
active enumeration tooling. The Auditor correctly distinguished profile
\emph{existence} from enumeration \emph{activity}. T1003.001 survived:
\texttt{procdump.exe} confirmed in \texttt{/Tools/SysInternals/} and
\texttt{spinlock.exe} confirmed in the WER ReportQueue crash dump.
\textbf{Lesson:} triage signals that fire on filesystem presence (binary
exists on path) without requiring execution evidence generate FPs that
the Auditor must correct. The corpus weight revision dampened
presence-only signals.

\paragraph{tdungan (earlier pipeline).}
Triage scored 67. After the Auditor confirmed both T1003.001 and
T1071.001 with physical artifact verification, adjusted score rose
to 85---reflecting IOC cross-match scoring applied to confirmed C2
infrastructure evidence absent from the generic sweep.
\textbf{Lesson:} confirmed IOC propagation from a prior host
increases the adjusted score when those IOCs appear on a new image.
This is the intended campaign-mode behavior; the score increase is
not a measurement artifact.

\subsection{Evidence Provenance}

All disk images were acquired by SANS using FTK Imager (ADI~3.3.0.5) on
2015-08-18 as part of the Stark Research Labs intrusion case.
Acquisition hashes are embedded in each E01 and verified read-only via
\texttt{ewfinfo} from \texttt{reports/chain\_of\_custody.json}.

\begin{table}[ht]
\centering
\caption{Disk image acquisition hashes (FTK Imager, 2015-08-18).
  Source: EWF acquisition metadata, \texttt{reports/chain\_of\_custody.json}.}
\label{tab:coc}
\small
\begin{tabular}{@{}llll@{}}
\toprule
Host (IP)         & Evi.\,\# & MD5 (acquisition) & SHA-1 (acquisition) \\
\midrule
nfury (10.3.58.6) & nfury-002 & \texttt{a98416e6\ldots} & \texttt{829553fd\ldots} \\
\bottomrule
\end{tabular}
\end{table}

\FloatBarrier
%% ── 6. Sigma Rule Export ────────────────────────────────────────────────────
\section{Sigma Rule Export}
\label{sec:sigma}

Adversarially validated rules are exported as Sigma YAML via
\texttt{sigma\_exporter.py}. Each rule embeds an
\texttt{adversa\_metadata} block containing the \emph{bypass rate}—
the fraction of \num{2031} Red Agent evasion attempts that evaded
that signal. No manually authored Sigma rule receives this level
of adversarial pressure before production. The exporter maps each
signal type to the correct Sigma field:

\begin{itemize}\setlength\itemsep{0pt}
  \item Registry path $\rightarrow$ \texttt{TargetObject|contains}
  \item IP address $\rightarrow$ \texttt{DestinationIp}
  \item Process name $\rightarrow$ \texttt{Image|endswith}
  \item General keyword $\rightarrow$ \texttt{EventData|contains}
\end{itemize}

\Cref{lst:sigma} shows the exported rule for T1003.001, derived from
real Mordor LSASS-access events with \texttt{GrantedAccess} values
extracted by grounded learning.

\begin{listing}[ht]
\begin{minted}{yaml}
title: find-evil — LSASS Credential Dumping (Adversarially Hardened)
id: fe-t1003-001
status: experimental
description: >
  Detects LSASS memory access patterns extracted from real
  OTRF/Mordor Sysmon telemetry (49,519 events).
  Adversarially hardened against 266 Red Agent evasion
  attempts over 4,500 training iterations.
adversa_metadata:
  bypass_rate: 0.68
  signal_source: grounded
  protected_ioc: true
  iterations_hardened: 4500
  patterns_learned: 16
detection:
  selection:
    EventID: 10
    TargetImage|endswith: '\lsass.exe'
    GrantedAccess|contains:
      - '0x1fffff'
      - '0x1410'
      - '0x1010'
  condition: selection
falsepositives:
  - Legitimate AV or EDR products
level: high
tags:
  - attack.credential_access
  - attack.t1003.001
\end{minted}
\caption{Adversarially hardened Sigma rule for T1003.001 with embedded bypass
rate. The \texttt{adversa\_metadata} block gives analysts a
quantitative hardening metric absent from all manually authored rules.
\texttt{GrantedAccess} values (\texttt{0x1fffff}, \texttt{0x1410},
\texttt{0x1010}) were extracted by grounded learning from real Mordor
LSASS-access events—not hand-authored.}
\label{lst:sigma}
\end{listing}

%% ── 7. Security Model ───────────────────────────────────────────────────────
\section{Security Model}
\label{sec:security}

The MCP server (\texttt{sift\_server.py}) enforces evidence integrity
at four independent layers before any shell command executes.
The security model is not \emph{trust Claude}—it is \emph{make bad
actions structurally impossible}.

\textbf{Layer~1 — Hard-blocked strings.} \texttt{wget}, \texttt{curl},
\texttt{nc}, \texttt{sudo}, \texttt{shred}, \texttt{\$(},
and backtick are rejected unconditionally. Command substitution
(\texttt{\$()} and backticks) is specifically blocked because it allows
an attacker-controlled string in a log file to inject a second command
as an argument to a permitted binary.

\textbf{Layer~2 — Segmented allowlist.} The command is split on
\texttt{|} and each segment tokenised with \texttt{shlex.split()},
which handles quoted escapes correctly. The leading binary must appear
in the explicit allowlist of SIFT forensic tools (50+ entries).
Anything unlisted is rejected.

\textbf{Layer~3 — Quote-aware pipeline split.} Before Layer~2's allowlist
check, the pipeline is split by a quote-aware parser rather than a
naive regex. The parser tracks single-quoted substrings and treats
\texttt{|} characters inside quotes as literal argument characters, not
pipeline separators. This is necessary because standard forensic
invocations such as \texttt{grep -iE '(http|https|ftp)'} contain
\texttt{|} inside the pattern argument; a naive split would fragment the
command and misidentify \texttt{https} as an unlisted binary.

\textbf{Layer~4 — Path-restricted redirection.} Redirection targets
are resolved with \texttt{os.path.realpath()} to defeat symlink and
\texttt{../} traversals, then verified to fall inside
\texttt{\_REPORTS}. Redirection to \texttt{/dev/null}, evidence
directories, or system paths is structurally impossible.

Every execution decision is written to an append-only audit log before
the command runs, providing a full chain of custody for every tool call.

%% ── 8. Ablation Study ───────────────────────────────────────────────────────
\section{Ablation Study}
\label{sec:ablation}

\subsection{Design}

To isolate the contribution of ASL-trained signals from hardcoded IOCs,
we ran a deterministic ablation over a 20\% holdout of the Mordor
dataset (last 20\% per technique by JSONL order; no shuffling).
Three scoring conditions were evaluated against the same
\num{9903}-event holdout (source:
\texttt{analysis/ablation\_study.py}~$\to$~\texttt{reports/ablation\_study.json}):

\begin{itemize}\setlength\itemsep{2pt}
  \item \textbf{Combined} — current system: conjunction scoring with
    protected-signal half-weight (§3.4).
  \item \textbf{IOC-only} — only signals in the \texttt{PROTECTED\_SIGNALS}
    list score; any single IOC match awards full weight. Represents a
    baseline lookup-table detector.
  \item \textbf{ASL-only} — all 83 learned signals, no protected status;
    strict conjunction (two or more signals required). Represents the
    pure learning contribution.
\end{itemize}

\subsection{Results}

\begin{table}[ht]
\centering
\caption{Ablation study on 20\% held-out Mordor events
  (source: \texttt{reports/ablation\_study.json}).
  \emph{Presence} = fraction of events where $\geq$1~signal matched the
  formatted artifact string, regardless of threshold.
  \emph{Detection} = fraction scoring $\geq$~40 (conjunction threshold).}
\label{tab:ablation}
\small
\begin{tabular}{@{}lrrrrr@{}}
\toprule
Condition & Presence & Detection & F1 & FP rate \\
\midrule
Combined  & 61.6\% & 5.6\%  & 0.105 & 12.5\% \\
IOC-only  & 61.6\% & 2.0\%  & 0.040 & 12.5\% \\
ASL-only  & 61.6\% & 4.1\%  & 0.079 &  0.0\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Interpretation}

Three findings warrant explanation.

\textbf{ASL doubles IOC coverage.} ASL-only detection (4.1\%) is
more than double IOC-only (2.0\%), demonstrating that grounded signal
learning contributes independently of the forensic IOC seed.

\textbf{Conjunction is doing work.} Signal presence is 61.6\% across all
conditions---meaning the signals are broadly sensitive---but scored
detection falls to 2--6\% because the conjunction threshold (§3.4)
requires at least two signals per technique before awarding any score.
The presence-to-detection gap is a design property, not noise.

\textbf{ASL removes false positives.} ASL-only achieves 0\% FP on the
benign pool. The 12.5\% FP in combined and IOC-only comes from
single-IOC protected-signal half-weight scoring, which fires on the
one benign event containing ``lsass'' in its registry path. Strict
conjunction eliminates this.

\textbf{Methodology note.} The training-loop detection rate (76\%,
ACCURACY.md) measures a different quantity: cumulative detections over
2,122 randomly sampled events during training, using the \emph{evolving}
signal set (which grew from 0 to 151 signals during training) with raw
event context available for grounded learning. The holdout evaluation
here uses the final pruned 83-signal set scored on formatted Sysmon
strings only. The Mordor JSONL files also contain predominantly
background Windows telemetry (EventID 800/4103 PowerShell pipeline events
account for 19.5\% of all events but format to bare ``EventID=800'' strings
because their attack content lives in \texttt{Message}/\texttt{Payload}
fields not extracted by \texttt{\_format\_event}). These methodological
differences are documented in \texttt{reports/ablation\_study.json}.

%% ── 9. Limitations ──────────────────────────────────────────────────────────
\section{Limitations}

\textbf{False-positive rate.} At 4,500 iterations, the FP rate on
benign events is 87\% (1,163 false positives on 1,333 benign tests).
An 87\% FP rate makes the current system unsuitable for production
deployment against live endpoints—in a 1,000-endpoint environment it
would generate approximately 870 analyst reviews per sweep. It is
suitable for forensic triage of known-suspicious disk images where the
base rate of compromise is high. The Forensic Auditor mitigates this in
deployment: on nfury, the Auditor correctly confirmed 15 of 19 triage
detections and refuted 4 memory-only signals, reducing analyst
ambiguity from 19 unverified flags to 15 confirmed findings with
artifact citations.

The rate is explained structurally by two factors. First, a training
imbalance: the Mordor dataset provides \num{49519} attack events
against 8 benign templates sampled at 30\%---the discriminator
optimises for recall. Second, pool-separation analysis of the
83-signal library shows 30\% of signals appear in the benign baseline
and 34\% are campaign-specific IOCs that overfit to this intrusion's
tooling; together these 64\% of signals either fire on benign events
or produce zero hits against a novel campaign. The remaining 36\% are
discriminative by construction. Pool separation against a real benign
baseline (see §10) is the structural fix; conjunction scoring (§3.4)
reduces additive FP accumulation as an interim mitigation.

\textbf{Shared model limitation.} Red and Blue share the same
underlying LLM (Claude). Claude cannot simulate a zero-day technique
it has never encountered; it generates plausible evasions of known
techniques, not novel ones. A nation-state zero-day would not be
caught until it appeared in training data.

\textbf{T1071.001 excluded from ML metrics.} C2 web protocol detection
relies entirely on IOC-based protected signals (confirmed C2 IPs from
the case investigation). It is not subject to the adversarial loop and
is excluded from the per-technique accuracy table.

%% ── 10. Future Work ─────────────────────────────────────────────────────────
\section{Future Work}

\begin{itemize}
  \item \textbf{Pool-separation signal extraction} — the immediate
        architectural priority. Replace grounded learning's per-event
        extraction with set-theoretic discrimination:
        $\text{signals}(T) = \text{values}(\text{Mordor}[T]) \setminus
        \text{values}(\text{BETH})$.
        A value is admitted as a signal only if it appears in documented
        attack telemetry for technique $T$ and \emph{never} in a
        real-world benign baseline. This makes false signal introduction
        structurally impossible and makes the 34\% campaign-specific IOC
        fraction identifiable at training time rather than after
        deployment.
  \item \textbf{Coverage expansion} — from 8 to 50+ MITRE techniques
        via automatic Mordor dataset enumeration through MSTICPy
        \texttt{MordorDriver}.
  \item \textbf{Memory forensics integration} — Volatility~3 plugin
        routing through the MCP layer for process injection and rootkit
        detection techniques not visible on disk.
  \item \textbf{Timeline correlation} — Plaso super-timeline filtered to
        confirmed technique time windows, scoring temporal clustering of
        artifacts as corroborating evidence.
  \item \textbf{Atomic Red Team VM integration} — real adversary-tool
        execution against a live Windows VM for truly novel Red Agent
        evasions beyond LLM-generated variants.
  \item \textbf{Neural network detection with auditor admissibility layer.}
        The legal battleground for forensic AI admissibility is already
        established. TrueAllele (probabilistic DNA mixture interpretation)
        and COMPAS (recidivism scoring) have been challenged in court on
        black-box grounds---defendants argued the inability to inspect
        model internals violated due process. A deep neural network
        trained on Mordor telemetry would outperform log-odds ratios on
        detection rate, but its weights are not explainable in the way
        a court or chain-of-custody review requires. The ADVERSA audit
        architecture is the direct answer: a black-box detection model
        can be deployed as the triage layer if---and only if---every
        flagged finding is subsequently verified by a Forensic Auditor
        that reads physical bytes off disk and produces an artifact
        citation traceable to a specific tool call. The NN provides the
        detection rate; the Auditor provides the admissibility. This
        separation is not a workaround---it is the correct architecture
        for production forensic AI.
\end{itemize}

%% ── 11. Conclusion ──────────────────────────────────────────────────────────
\section{Conclusion}

The domain-gap recovery documented in \cref{fig:curve} is a genuine
research finding: most security AI systems train on synthetic logs and
report inflated accuracy. find-evil deliberately switched to real
Sysmon telemetry, documented the collapse to 10\% detection at
iteration~10, and measured autonomous recovery to 76\% detection and
F1~=~0.72 over \num{4500} iterations with no human intervention. The
\num{2031} adversarial evasion attempts embedded in the exported Sigma
rules give analysts a quantitative hardening metric that does not
exist in any manually authored rule set. Two hosts from an APT intrusion were investigated autonomously. On
nfury, the Forensic Auditor confirmed 15 of 19 triage detections and
refuted 4 memory-only signals; the complete attack chain---httppump
backdoor (\texttt{svchost.exe} in \texttt{\$Recycle.Bin}, timestomped,
C2 at \texttt{192.168.1.5/ads/}), injector (\texttt{a.exe},
127 \texttt{PAGE\_EXECUTE\_READWRITE} VADs), attacker account
(\texttt{SRL-Helpdesk}, Event~ID~4720), and PsExec lateral
movement---was characterized in 969\,s at \$14 cost. On tdungan,
run in campaign mode, 13 of 17 were confirmed; T1566 (Phishing)
identified the campaign initial access vector, and an identical
SRL-Helpdesk NTLM hash confirmed cross-host credential reuse.
Twenty-eight techniques confirmed across 36 detected, 8 refuted by
the Auditor---all within 30~minutes total, at under \$30 combined.

Every other approach gives defenders better tools. find-evil gives
defenders the same adaptive mechanism that makes AI attacks
dangerous—now working for the defense.

\FloatBarrier
%% ── 12. File Reference ──────────────────────────────────────────────────────
\section*{Architecture Reference}

\begin{table*}[ht]
\centering
\caption{find-evil source file roles.}
\begin{tabular}{@{}lp{0.62\linewidth}@{}}
\toprule
File & Role \\
\midrule
\texttt{brain.py}               & ASL orchestrator — ForensicBrain + BlueDiscriminator + training metrics \\
\texttt{mordor\_agent.py}       & Gen~3 Red Agent — loads \num{49519} real Sysmon events from OTRF Mordor \\
\texttt{msticpy\_red\_agent.py} & Training enhancement — MSTICPy dataset discovery (offline training only) \\
\texttt{msticpy\_enrichment.py} & Training enhancement — process/registry/network enrichment tokens (offline training only) \\
\texttt{pattern\_db.py}         & SQLite pattern store — versioned per-signal hit/miss counters and training-run history \\
\texttt{export\_patterns.py}    & Post-training — filters and exports signals above weight threshold \\
\texttt{sigma\_exporter.py}     & Post-training — field-mapped Sigma YAML with adversarial bypass rates \\
\texttt{investigate.py}         & Pipeline orchestrator — Triage Agent $\to$ Forensic Auditor $\to$ unified report \\
\texttt{blue\_agent.py}         & Triage Agent — Pass~1 generic SIFT sweep + Pass~2 agentic investigation loop \\
\texttt{auditor\_agent.py}      & Forensic Auditor — parallel \texttt{asyncio.gather} technique challenges \\
\texttt{sift\_server.py}        & MCP server — four-layer security boundary for all forensic tool execution \\
\texttt{html\_report.py}        & Report renderer — generates \texttt{\{host\}-report.html} from JSON artifacts \\
\texttt{extract\_iocs.py}       & IOC extractor — confirmed artifacts only; supports \texttt{--merge} for campaign correlation \\
\texttt{adversa-merge-iocs.sh}  & Campaign merge — deduplicates IOC files from multiple hosts \\
\texttt{adversa.sh}             & CLI entry point — API key, mount check, \texttt{--ioc-file}, \texttt{--no-synthesis} \\
\bottomrule
\end{tabular}
\end{table*}

\bibliographystyle{ACM-Reference-Format}
%% \bibliography{adversa}   %% uncomment when .bib file is present

\end{document}
